Meta-analysis

### 2019-11-07 05_MetaAnalysis.Rmd
Plotting model

anova(m8,m9) # 65 has a lower AIC but not evaluated as a significantly better model

summary(m9)

>>>>

anova(m8,m9) # m9 is significantly better model

summary(m9)
# m9_summary <- as.data.frame(coef(summary(m9)))
# m9_summary[1,1] <- 0
# m9_summary$treats <- row.names(m9_summary)
# 
# class(m9_summary)
# 
# 
# m9_summary %>%
#    ggplot(aes(x = treats, y = exp(Estimate)))+
#    geom_point()+
#    geom_linerange(ymin = exp(m9_summary[,1] - m9_summary[,2]),
#                   ymax = exp(m9_summary[,1] + m9_summary[,2]))+
#    geom_hline(yintercept = m9_summary[1,1])+
#    geom_rect(ymin = exp(m9_summary[1,1] - m9_summary[1,2]),
#              ymax = exp(m9_summary[1,1] + m9_summary[1,2]),
#              xmin = -Inf, xmax = -Inf,
#              fill = "red", alpha = 0.5)+
#    coord_flip()
# 
#
